\section{Taxi queue management}
As stated in the RASD, the taxi drivers are divided in city zones according to their current location. Each zone is served by a local queue of taxi driver which are enabled to pick the ride request and serve the clients. This section elaborates in detail how the queues are managed by the system.

The algorithm is run every time there is a new event which changes the order or the number of the elements in one of the system queues.

According to the type of event, the algorithm updates the queues moving, deleting or creating elements. There are several types of events:
\begin{enumerate}
	\item new request incomes; \label{event:new_req}
	\item taxi Driver accepts a request; \label{event:accepted_req}
	\item taxi Driver refuses a request; \label{event:refuses_req}
	\item taxi Driver changes zone; \label{event:changed_zone}
	\item taxi Driver changes his/her status. \label{event:changed_status}
\end{enumerate}
The input data are:
\begin{itemize}
	\item $Q_i$: list of FIFO queues, where $i$ is the zone of the correspondent queue.
	\item $e$: event which will change the queues.
	\item $OOS$: list of taxi drivers out of service.
	\item $B$: list of busy taxi drivers.
	\item $P$: list of taxi drivers with a pending ride.
\end{itemize}

The algorithm works differently accordingly with the input event. The alternatives are explained in the following subsections.

\subsection{Type \ref{event:new_req}, new request incomes}
The algorithm extracts the zone $z$ of the new incoming request, pops the first element of the $Q_z$ and inserts this element in $P$ list.

\subsection{Type \ref{event:accepted_req}, taxi driver accepts a request}
The algorithm extracts the taxi driver $t$ from the event and removes him/her from $P$. After that it inserts $t$ into $B$.

\subsection{Type \ref{event:refuses_req}, taxi driver refuses a request}
The algorithm extracts the taxi driver $t$ from the event and it removes him/her from $P$. After that it retrieves the taxi driver's actual zone $z$ and it pushes $t$ in $Q_z$.

\subsection{Type \ref{event:changed_zone}, taxi driver changes zone}
The algorithm extracts the taxi driver $t$, the previous zone $pz$ and the next zone $nz$ from the event and removes $t$ from $Q_{pz}$ and pushes $t$ into $Q_{nz}$.

\subsection{Type \ref{event:changed_status}, taxi driver changes status}
If the taxi driver $t$ changes his/her status from “not in service” to “in service”, the algorithm extracts the zone $z$ from the event, it removes $t$ from $OOS$ and pushes $t$ into $Q_z$.

If the taxi driver $t$ changes his/her status from “in service” to “not in service”, the algorithm extracts the zone $z$ from the event, it removes $t$ from $Q_z$ and pushes $t$ into $OOS$.
