\section{Taxi waiting calculation}
\label{sec:taxiwaiting}
When a passenger requests a taxi and his request is assigned to a taxi driver, the system tells the user the estimated time of arrival (ETA) of the taxi. This delay is computed by using the Google Maps Directions API~\cite{Google-Maps-Directions-API}, called as a service from the business logic layer.

The flow of events is as follows:
\begin{enumerate}
\item The passenger requests a taxi and sends his current position to the system.
\item The system looks for an available taxi driver in the same zone of the passenger.
\item The request is accepted by one taxi driver, who sends his current position to the application server.
\item \label{point-a} The application server computes the ETA by sending a request to Google Maps; the format of the request is specified in~\autoref{tab:gmaps-parameters}.
\item \label{point-b}The application server sends to the passenger the ETA, when required by the client.
\item Points \ref{point-a}, \ref{point-b} are repeated every 90 seconds until the taxi notifies that it has picked up the passenger.
\end{enumerate}

A detailed view of the sequential interaction among the components was shown in the runtime views, in~\autoref{fig:sequence-gmaps}.

The detailed API call sent to the Google Maps Directions API is shown in~\autoref{tab:gmaps-parameters}. We chose to adopt the pessimistic traffic model because, although taxi driver often have reserved lanes, it's best to leave some safety margin of time.

\begin{table}
    \centering
    \begin{tabular}{l p{0.5\textwidth}}
        \hline
        URL & \url{http://maps.googleapis.com/maps/api/directions/xml}\\
        \hline
        \texttt{origin} & GPS coordinates of the taxi driver\\
        \hline
        \texttt{destination} & GPS coordinates of the passenger\\
        \hline
        \texttt{key} & API key\\
        \hline
        \texttt{mode} & \texttt{driving}\\
        \hline
        \texttt{departure\_time} & \texttt{now}\\
        \hline
        \texttt{traffic\_model} & \texttt{pessimistic}\\
        \hline
    \end{tabular}
    \caption{Parameters of the Google Maps API call for the estimation of the waiting time.}
    \label{tab:gmaps-parameters}
\end{table}
