\subsection{User interfaces}

The user interfaces must satisfy the following UI constraints:
\begin{itemize}
    \item Web application
        \begin{enumerate}
        \item The web pages must adhere to the W3C standards. In particular, the software conforms to the HTML5~\cite{w3c-html5} and CSS~\cite{w3c-css} standards.
        \item The web pages must be accessible also by text-only browsers.
        \end{enumerate}
    \item Mobile app
        \begin{enumerate}
        	\item The iOS version must adhere to the iOS Human Interface Guidelines~\cite{apple-ios-hig}.
	\item The Android version must follow Android design guidelines~\cite{google-android-hig}.
        \end{enumerate}
     \item Server back-end
     	\begin{enumerate}
		\item The server back-end must be configurable by means of a configuration text file.
	\end{enumerate}
    \item Common to all interfaces:
    \begin{enumerate}
        \item The clients must have an UI that is accessible to disabled people.
        \item The interface must offer the possibility to choose the language used at all times.
        \item The first screen must ask the user to login in order to begin operations.
        \item A dashboard with links to every function shall be displayed in the home page in order to show the user the capabilities of the system and allow him to save time.
        \item The dashboard must be linked in every screen.
        \item The top bar must show the last taxi service called, with a link to a screen which displays the reserved taxi history.
        \item The compilation of data fields has to be made with suitable controls (multiple choice, date picker, text field, \ldots) in order to simplify the user's experience of the app.
        \item UI controls and views must be suitable for the input interface and the screen size.
    \end{enumerate}
\end{itemize}

\subsection{Hardware interfaces}

The client app must be able to access the GPS data of the user's phone.
It has to deal with security dialogs, authorization and platform-specific code.

\subsection{Software interfaces}
The system is built in a modular fashion: the core part of the system exposes public APIs allowing the building of new interfaces and modules.

For a detailed specification of the programmatic interfaces, see \autoref{sec:api}.

The required software products used by the back-end are:
\begin{itemize}
\item MySQL 5.7   \url{http://dev.mysql.com}
\item Java SE 8   \url{http://java.com}
\end{itemize}

\subsection{Communications interfaces}
The clients communicate with the server via HTTPS requests (port 443).
